HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex

\paragraph{Cost of Structural Annotation}

HMEANT structural annotation (semantic role labelling, SRL), similar to e.g.
PropBank
\parcite{palmer2010semantic}, is designed to be very simple and easy to explain
to lay annotators.
HUME relies on UCCA, which is arguably more abstract, harder to
explain, and thus more expensive to obtain.

On the other hand, HUME 
needs the semantic annotation
done once for a given source sentence, whereas for the HMEANT set-up, every new
MT output has to be structurally annotated.

>>>>

%
%\paragraph{Cost of Structural Annotation}
%
%HMEANT structural annotation (semantic role labelling, SRL), similar to e.g.
%PropBank
%\parcite{palmer2010semantic}, is designed to be very simple and easy to explain
%to lay annotators.
%HUME relies on UCCA, which is arguably more abstract, harder to
%explain, and thus more expensive to obtain.
%
%On the other hand, HUME 
%needs the semantic annotation
%done once for a given source sentence, whereas for the HMEANT set-up, every new
%MT output has to be structurally annotated.\oa{we can give some empirical data here.
